---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multimeter

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/multimeter)](https://CRAN.R-project.org/package=multimeter)
[![Codecov test coverage](https://codecov.io/gh/bvancil/multimeter/branch/main/graph/badge.svg)](https://codecov.io/gh/bvancil/multimeter?branch=main)
[![R-CMD-check](https://github.com/bvancil/multimeter/workflows/R-CMD-check/badge.svg)](https://github.com/bvancil/multimeter/actions)
<!-- badges: end -->

Inspect data pipelines (especially magrittr pipelines) for before-after changes during tricky operations.

## Installation

You can install the latest development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("bvancil/multimeter")
```

## Example

The basic `Multimeter` class powers the `mm_get_*_meter()` functions, which are easier to use.

```{r library}
library(dplyr)
library(multimeter)
```

### Monitoring missingness during operations

```{r missingness}
# Function to intentionally introduce some NAs
maybe_na <- function(x, prob = 0.2) {
  n <- base::length(x)
  missing_of_type_x <- vctrs::vec_cast(NA, to = vctrs::vec_ptype(x))
  dplyr::if_else(stats::runif(n) < prob, missing_of_type_x, x)
}

missing_meter <- multimeter::mm_get_missing_meter()
set.seed(2021L + 06L + 28L)
starwars2 <- dplyr::starwars %>%
  missing_meter$probe() %>% 
  dplyr::mutate(homeworld = maybe_na(homeworld)) %>% 
  missing_meter$probe()
```

You can access this comparison through

```{r missingness2}
missing_meter$comparison
```

### Summarizing changes in specific columns

```{r value}
value_meter <- multimeter::mm_get_value_meter()
mtcars2 <- mtcars %>%
  value_meter$probe(cyl) %>%
  dplyr::mutate(square_error_from_five = (cyl - 5)^2) %>%
  value_meter$probe(square_error_from_five)
```

You can access a summary of changed column values and frequency counts through

```{r value2}
value_meter$comparison
```

It would be nice to do this automatically, perhaps by decorating `dplyr::mutate`.

## Contributing

Run to install development packages:

``` r
renv::restore()
```

Run before committing:

``` r
source("R/dev/before_commit.R")
```

## Code of Conduct
  
Please note that the multimeter project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

